Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
fix my email address

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciej Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de, antocuni@gmail.com, fijal@merlinux.eu,
           samuele.pedroni@gmail.com, arigo@tunes.org}

>>>>

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciej Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de, anto.cuni@gmail.com, fijal@merlinux.eu,
           samuele.pedroni@gmail.com, arigo@tunes.org}
